Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
Dediction tree for CCS

\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
  open transition $OT_{11}$ of \texttt{CCS} (see example page
  \pageref{OT:ccs-composed}).
%  \TODO{Eric: change for a deduction tree of CCS expression}
\ERIC{  The rule uses TR1 for the $l$ transition of $C_1$ and for the $b$ transition of $C_2$, uses an action $b_P$ of hole $P$, then combines the result using the second vector of the PN2 sub-pNet, and the third vector of the top node. This yield a final $\tau$ transition. The deduction tree in the figure shows how the predicate are generated in this process.
}

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\xrightarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \xrightarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
  \label{usingrules:OT2}
\end{figure}

>>>>

\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
  open transition $OT_{11}$ of \texttt{CCS} (see example page
  \pageref{OT:ccs-composed}).
%  \TODO{Eric: change for a deduction tree of CCS expression}
\ERIC{  The proof tree uses TR1 for the $l$ transition of $C_1$ and for the
  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, then
  combines the results using the second vector of the PN2 sub-pNet, and
  the third vector of the top node. This yields a final $\tau$
  transition. The deduction tree in the figure shows how the
  predicates are generated in this process. 
}

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
      {
          \inferrule
              {1 \xrightarrow {l}_{C_1} 1}
              {C_1
                \models
                \openrule
                      {1 \xrightarrow{l}_{C_1} 1}
                      {\ostate{1}\xrightarrow{1}\ostate{1}}
              }
        }
        {\textrm{a:P}
          \models
            \openrule{
              1 \xrightarrow {l}_{C_1} 1,\,
              \{\xrightarrow{b_P}_P\},\, b_P\neq l}
                      {\ostate{1}\xrightarrow{b_P}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
          \inferrule
              {0 \xrightarrow{b}_{C_2} 1}
              {C_4
                \models
                \openrule
                      {0 \xrightarrow{b}_{C_2} 0,\, b\neq r}
                      {\ostate{0}\xrightarrow{b}\ostate{1}}
              }
        }
        {
          \textrm{b:Q}\models
              \openrule
                  { 0 \xrightarrow {b}_{C_2} 1,\, \ b\neq r}
                  {\ostate{0}\xrightarrow{b}\ostate{1}}
        }   
    }
    {
     \textrm{PN1}
     \models
        \openrule{
                       1 \xrightarrow{l}_{C_1} 1 ~~
                       0 \xrightarrow{b}_{C_2} 1 ~~
                       \{ \xrightarrow{b_P}_{P} \}               ~~
                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
                      }
     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
  \label{usingrules:OT2}
\end{figure}
